---
title: "Portfolio1"
author: "Xuanyu Lyu"
date: "2/5/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(remotes)
```

# Two functions with active objects inside the functions

My first portfolio is two functions that I used for Laura's limit breaking project. What I learnt by coding those two functions is two approaches to make active parameters inside a function.

## the First function
The first function is to get costomized dataframe with specific parenting style, the year of the relative parenting styles and the year of behaviors. In this function I used the paste() function to achieve the activity of parameters, which is the specific columns with assigned years or parenting styles.And it's a mandotory function for the second function to operize. 


```{r function1}

# the function for getting comparison dataframe
get_a_df <- function(Ptype.x, Ptype.y,
                     yearPtype = 1997, yearBtype = 1997){
  df_temp <- df_double_clean[1,]
  j <- 1
  var_PtypeS1 = paste("Pstyle_", yearPtype, "_S1", sep = "")
  var_PtypeS2 = paste("Pstyle_", yearPtype, "_S2", sep = "")
  for(i in 1:nrow(df_double_clean)){
    if(is.na(df_double_clean[i,var_PtypeS1]) == TRUE | is.na(df_double_clean[i,var_PtypeS2]) == TRUE){
      next
    }
    if(df_double_clean[i,var_PtypeS1] == Ptype.x & df_double_clean[i,var_PtypeS2] == Ptype.y | df_double_clean[i,var_PtypeS2] == Ptype.x & df_double_clean[i,var_PtypeS1] == Ptype.y  ){
      df_temp[j,] = df_double_clean[i,]
      j = j+1
      next
    }
  }
  
  df_Ptype <- df_temp[,2:9] %>% select(grep(as.character(yearPtype), names(df_temp[,2:9])))
  df_Btype <- df_temp[,10:ncol(df_temp)] %>% select(grep(as.character(yearBtype), names(df_temp[,10:ncol(df_temp)])))
  
  df_target <- cbind("pairid" = df_temp[,1], df_Ptype, df_Btype)
  
  
  return(df_target)
}




```

## the Second function
The second function is designed to get the results of discordant kinship model for a specific year and a specific combination of parenting styles. I used the "{{}}" and ":=" to call the active objects produced in the same function. For example, I created a character factor called "ave" and I want to use the value of this factor rather than the "ave" charactor in the mutate() of dplyr. By default, the metate() will treat ave as "ave" and doesn't call its value. But with the two symbols, we can create new columns named by the value of ave rather than "ave". 



```{r pressure}
### a function to get results


getResults <- function(yearPS, PS1, PS2, Btype){
  df1 = merge(get_a_df(PS1, PS1, yearPS, 1997),y = df_double_clean, by = "pairid")[,c(1:3,34:36,49:51)]
  df2 = merge(get_a_df(PS1, PS2, yearPS, 1997),y = df_double_clean, by = "pairid")[,c(1:3,34:36,49:51)]
  df3 = merge(get_a_df(PS2, PS2, yearPS, 1997),y = df_double_clean, by = "pairid")[,c(1:3,34:36,49:51)]
  
  df1$group = as.factor(paste(PS1,"_",PS1, sep = ""))
  df2$group = as.factor(paste(PS1,"_",PS2, sep = ""))
  df3$group = as.factor(paste(PS2,"_",PS2, sep = ""))
  
  df_PS12 = rbind(df1,df2,df3)
  colnames(df_PS12)[2:3] = c(paste("Pstyle",yearPS,"_S1", sep = ""),
                             paste("Pstyle",yearPS,"_S2", sep = ""))
  if(grepl(Btype,"staylate")){
    c1 = 4
    c2 = 7
  } else if(grepl(Btype,"tvkind")){
    c1 = 5
    c2 = 8
  } else if(grepl(Btype,"hangout")){
    c1 = 6
    c2 = 9
  } else{
    stop("should be staylate, tvkind or hangout")
  }
  df_model = df_PS12 |> filter(!is.na(df_PS12[,c1]) & !is.na(df_PS12[,c2]))
  diffe = paste("diff",Btype, sep = "_")
  ave = paste("average",Btype, sep = "_")
  df_model = df_model |> mutate({{diffe}} := df_model[,c1] - df_model[,c2],{{ave}} := (df_model[,c1] + df_model[,c2])/2)
  fomula = paste(diffe, "~group+",ave,sep = "")
  mySummary = df_model |> lm(formula =  as.formula(fomula)) |> summary()
  return(mySummary)
}
```


