---
title: "Lab 09 - Grading the professor, Pt. 1"
author: "Xuanyu"
date: "04/07/2022"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)
```

### Exercise 1

It's negatively skewed.

```{r}
df <- evals
hist(df$score)
```


### Exercise 2

```{r}
ggplot(df, aes(x=score, y=bty_avg)) +
    geom_point(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)

```

### Exercise 3

```{r}
ggplot(df, aes(x=score, y=bty_avg)) +
    geom_jitter(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)
```

jitter provides some random variation to the plot so the dots won't overlap with each other although they have the same values.

### Exercise 4

```{r}
m_bty <- lm(df$score ~ df$bty_avg)
summary(m_bty)
```

### Exercise 5

```{r}
ggplot(df, aes(x=score, y=bty_avg)) +
    geom_jitter(shape=1) +    # Use hollow circles
    geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)
```

### Exercise 6

Higher rating on beauty will lead to higher score. 

### Exercise 7

When beauty is 0, the predicted score if 3.88.

### Exercise 8

The R2 is .04, which means 4% of the variance of the score is explained by beauty. 

### Exercise 9

```{r}
m_gen <- lm(df$score ~ df$gender)
summary(m_gen)
```

The mean score for female is 4.09, and the mean score for male is significantly .14 higher than female.  

### Exercise 10

For male score = 4.09 + 1 * 0.14
For female score = 4.09 + 0 * 1.14

### Exercise 11

```{r}
m_rank <- lm(df$score ~ df$rank)
summary(m_rank)
df |> group_by(rank) |> summarise(mean(score))
```

The average score of teaching professor is 4.28. And the tenure track professor and tenured professor are -.13 and -.15 points lower than teaching professor separately. 
### Exercise 12

```{r}

df$rank_relevel <- df$rank
df$rank_relevel <- relevel(df$rank_relevel, "tenure track")
m_rank_relevel <- lm(df$score ~ df$rank_relevel)
summary(m_rank_relevel)
df |> group_by(rank_relevel) |> summarise(mean(score))

```

### Exercise 13

There's no significant difference between tenured track professors and teaching or tenured on scores. 

### Exercise 14

```{r}
df <- df |> mutate(tenure_eligible = recode_factor(rank, "teaching" = "no", "tenure track" = "yes", "tenured" = "yes"))

```

### Exercise 15

```{r}
m_tenure_eligible <- lm(df$score ~ df$tenure_eligible)
summary(m_tenure_eligible)
```
