---
title: "Lab 05 - La Quinta is Spanish for next to Denny's, Pt. 2"
author: "Xuanyu"
date: "02/06/2022"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox) 
```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")
df_denny <- dennys
df_laquinta <- laquinta
```

### Exercise 1

```{r}
df_dennyAK <- df_denny %>%
  filter(state == "AK")
nrow(df_dennyAK)
```


### Exercise 2

```{r}
df_laquintaAK <- df_laquinta %>%
  filter(state == "AK")
nrow(df_laquintaAK)
```

### Exercise 3
we need to compute 6 different combinations of the branches.

```{r}
dn_lq_ak <- full_join(df_dennyAK, df_laquintaAK, by = "state")
dn_lq_ak
```



### Exercise 4

6 rows in the new dataframe. And all info excepts state are duplicated into two columns corresponding to the two brands.

```{r}
haversine <- function(long1, lat1, long2, lat2, round = 3) {
  # convert to radians
  long1 = long1 * pi / 180
  lat1  = lat1  * pi / 180
  long2 = long2 * pi / 180
  lat2  = lat2  * pi / 180
  
  R = 6371 # Earth mean radius in km
  
  a = sin((lat2 - lat1)/2)^2 + cos(lat1) * cos(lat2) * sin((long2 - long1)/2)^2
  d = R * 2 * asin(sqrt(a))
  
  return( round(d,round) ) # distance in km
}
```


### Exercise 5

we need to use mutate function
      

### Exercise 6

```{r}
dn_lq_ak <- dn_lq_ak |> mutate(distance = haversine(longitude.x, latitude.x, longitude.y, latitude.y))
```

### Exercise 7
```{r}
dn_lq_ak_mindist <- dn_lq_ak %>%
  group_by(address.x) %>%
  summarize(closest = min(distance))
```

### Exercise 8
```{r}
dn_lq_ak_mindist |> summarise(mean(closest))
dn_lq_ak_mindist |> ggplot(mapping = aes(x=closest))+
      geom_histogram(binwidth = 5)+theme_light()
```


### Exercise 9
```{r}
df_dennyNC <- df_denny %>%
  filter(state == "NC")
nrow(df_dennyNC)

df_laquintaNC <- df_laquinta %>%
  filter(state == "NC")
nrow(df_laquintaNC)

dn_lq_NC <- full_join(df_dennyNC, df_laquintaNC, by = "state")
dn_lq_NC <- dn_lq_NC |> mutate(distance = haversine(longitude.x, latitude.x, longitude.y, latitude.y))
dn_lq_NC_mindist <- dn_lq_NC %>%
  group_by(address.x) %>%
  summarize(closest = min(distance))

dn_lq_NC_mindist |> summarise(mean(closest))
dn_lq_NC_mindist |> ggplot(mapping = aes(x=closest))+
      geom_histogram(binwidth = 15)+theme_light()
```


### Exercise 10
```{r}
df_dennyTX <- df_denny %>%
  filter(state == "TX")
nrow(df_dennyTX)

df_laquintaTX <- df_laquinta %>%
  filter(state == "TX")
nrow(df_laquintaTX)

dn_lq_TX <- full_join(df_dennyTX, df_laquintaTX, by = "state")
dn_lq_TX <- dn_lq_TX |> mutate(distaTXe = haversine(longitude.x, latitude.x, longitude.y, latitude.y))
dn_lq_TX_mindist <- dn_lq_TX %>%
  group_by(address.x) %>%
  summarize(closest = min(distaTXe))

dn_lq_TX_mindist |> summarise(mean(closest))
dn_lq_TX_mindist |> ggplot(mapping = aes(x=closest))+
      geom_histogram(binwidth = 3)+theme_light()
```

### Exercise 11
```{r}
df_dennyCA <- df_denny %>%
  filter(state == "CA")
nrow(df_dennyCA)

df_laquintaCA <- df_laquinta %>%
  filter(state == "CA")
nrow(df_laquintaCA)

dn_lq_CA <- full_join(df_dennyCA, df_laquintaCA, by = "state")
dn_lq_CA <- dn_lq_CA |> mutate(distaCAe = haversine(longitude.x, latitude.x, longitude.y, latitude.y))
dn_lq_CA_mindist <- dn_lq_CA %>%
  group_by(address.x) %>%
  summarize(closest = min(distaCAe))

dn_lq_CA_mindist |> summarise(mean(closest))
dn_lq_CA_mindist |> ggplot(mapping = aes(x=closest))+
      geom_histogram(binwidth = 5)+theme_light()
```


### Exercise 12
The state Mitch Hedberg’s joke most likely to hold true is Alaska, where their only 2 laquintas and 3 dennys. And the data clearly shows that they are opened pretty near to each other. Maybe it's due to the limited population of Alaska and they are all gathered in the downtown of Alaska's capital. Also in CA and TX, which are two states have the greatest amount of branches among all states, the distance between laquintas and dennys are mostly very small (less than 5 kilometers). But in a far-away state, like NC, the intergrowth pattern of two brands is not salient. 
