---
title: "Lab 01 - Hello R"
author: "Xuanyu"
date: "01/12/2022"
output: 
  github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

There's 1846 rows and 3 columns in the data file. Three variables including the names of 13 datasets, the x value and the y values. 

### Exercise 2

The plot of the dino dataset

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation in the dino dataset. 

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

The plot in the star dataset



```{r plot-star, fig.height=3, fig.width=3}
star_data <- datasaurus_dozen %>% filter(dataset == "star")
star_data %>% ggplot(mapping = aes(x,y)) + geom_point()
```

The correlation coefficient in the star dataset. The correlation coefficient is quite similar to the one in the dino dataset.

```{r cor-star}
star_data %>% summarise(r = cor(x,y)) 
```

### Exercise 4

The plot in the circle dataset

```{r plot-circle, fig.height=3, fig.width=3}
circle_data <- datasaurus_dozen %>% filter(dataset == "circle")
circle_data %>% ggplot(mapping = aes(x,y)) + geom_point()
```

The correlation coefficient in the circle dataset. The coefficient is a little greater than the previous two. 

```{r cor-circle}
circle_data %>% summarise(r = cor(x,y)) 
```

### Exercise 5

The plot for all datasets

```{r plot for all, fig.height=4, fig.width=4}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 4) +
  theme(legend.position = "none")
```

The r coeffcients for all datasets

```{r coefficients for all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
    print(13)
```




## Bonus Tips by Yoo Ri
### Thanks Yoo Ri! *--Xuanyu*
Here are some helpful tips :) 

* filter() is for extracting rows

* group_by() is for grouping datasets by assigned column 
* ungroup() cancels the grouping 

* summarize()  is often used with group_by(). This function can print the output according to the group_by().

* facet_grid(y~x,...) creates a grid with variable y as a row, variable x as a column  
* facet_wrap(x,... ) is useful when there is only one variable
