---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Xuanyu"
date: "02/06/2022"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox) 
```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")
```

### Exercise 1

```{r denny}
df_denny <- dennys
df_laquinta <- laquinta
nrow(df_denny)
ncol(df_denny)
head(df_denny)
```

Each row in df_denny is a branch of dennys.The variables include address, city, state, zip code and the longitude and latitude of each brance

### Exercise 2

```{r laquinta}
nrow(df_laquinta)
ncol(df_laquinta)
head(df_laquinta)
```

The dimensions in laquinta dataset is about the same as the dennys.

### Exercise 3

The branches of dennys are all in the US but the branches of laquinta are distributed across the world.

### Exercise 4

Some ways to filter the non-US branches:
1. Use the zip
2. Use the longitude and latitude
3. Use the name of state

### Exercise 5


```{r}
df_denny |> filter(!(state %in% states$abbreviation))
```

No branches of dennies are outside of the US

### Exercise 6

```{r}
df_denny <- df_denny %>%
  mutate(country = "United States")
```

 
### Exercise 7

```{r}

df_laquinta |> filter(!(state %in% states$abbreviation))

```
### Exercise 8

```{r}

df_laquinta <- df_laquinta %>%
  mutate(country = case_when(
    state %in% states$abbreviation     ~ "United States",
    state %in% c("ON", "BC") ~ "Canada",
    state == "ANT"           ~ "Colombia",
    TRUE ~ "other"
  ))

```
### Exercise 9

```{r}

df_laquinta %>%
  count(state) %>%
      arrange(desc(n)) |>
  inner_join(states, by = c("state" = "abbreviation"))

```

Texas has the greatest amount of the branches. 

### Exercise 10

```{r}

df_laquinta %>%
  count(state) %>%
            inner_join(states, by = c("state" = "abbreviation")) |>
                  mutate(perSM = n*1000/area)|>
                        arrange(desc(perSM)) 
```

Rowde Island and Florida have the greatest amount of laquinta per thousand square miles.

```{r}

df_denny %>%
  count(state) %>%
            inner_join(states, by = c("state" = "abbreviation")) |>
                  mutate(perSM = n*1000/area)|>
                        arrange(desc(perSM)) 
```

DC have the greatest amount of dennys per thousand square miles.

### Exercise 11
```{r}
df_denny <- df_denny %>%
  mutate(establishment = "Denny's")
df_laquinta <- df_laquinta %>%
  mutate(establishment = "La Quinta")
df_dm <- bind_rows(df_denny,df_laquinta)
ggplot(df_dm, mapping = aes(x = longitude, y = latitude, color = establishment)) +
  geom_point()
```
### Exercise 12
```{r}

p1 <- df_dm |> filter(state == "NC") |>
      ggplot(mapping = aes(x = longitude, y = latitude, color = establishment))+
      geom_point(alpha = 0.7,size=2)
p1 + theme_light()

p2 <- df_dm |> filter(state == "TX") |>
      ggplot(mapping = aes(x = longitude, y = latitude, color = establishment))+
      geom_point(alpha = 0.5,size=1.5)

p2 + theme_light()
```
