---
title: "Lab 08 - Conveying the right message through visualisation"
author: "Xuanyu"
date: "04/07/2022"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercise 1

```{r}
df <- tribble(
  ~date, ~countM,~countU,
  "7/12/2020", 26, 10,
  "7/13/2020",20 , 9,
  "7/14/2020",20 , 9,
  "7/15/2020",21 , 10,
  "7/16/2020", 20, 10,
  "7/17/2020", 20, 9,
  "7/18/2020", 21, 9,
  "7/19/2020", 20, 9,
  "7/20/2020", 21, 8,
  "7/21/2020", 22, 8,
  "7/22/2020", 20, 8,
  "7/23/2020", 20, 8,
  "7/24/2020", 21, 10,
  "7/25/2020", 19, 10,
  "7/26/2020", 20, 10,
  "7/27/2020", 17, 9.5,
  "7/28/2020", 16, 9.5,
  "7/29/2020", 16, 9.5,
  "7/30/2020", 16, 10,
  "7/31/2020", 16, 9,
  "8/1/2020", 16, 9,
  "8/2/2020", 16, 9,
  "8/3/2020", 16, 9
)
df$date <- as.Date(df$date, format = "%m/%d/%y")
```


### Exercise 2

...
```{r}
library("reshape2")  
df_long <- df |> melt(id = "date")
df_long |> ggplot(mapping = aes(x = date, y = value)) + 
      geom_line(aes(color = variable), size = 1.5)+
      scale_color_manual(values = c("darkred", "steelblue"))
```

### Exercise 3

In the original version, they put the two lines onto two different scales so intuitively they were about the same levels but in fact the masked county had much higher case rate than unmasked county.

### Exercise 4

Well the data seems counter-intuitive as it makes no sense that the masked counties should have higher rate of covid. But to think this deeply, it may be due to the fact that the masked counties are more politically liberal. And normally, big cities are more liberal than small town and meanwhile big cities have greater population density which make them more easy for the virus to spread. 

