---
title: "Lab 10 - Grading the professor, Pt. 2"
author: "Xuanyu"
date: "04/08/2022"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)
```

### Exercise 1

```{r}
df <- evals
lm(score~bty_avg, data = df) |> summary()
```


### Exercise 2

```{r}
lm(score~bty_avg+gender, data = df) |> summary()
df |> group_by(gender) |> summarise(mean(score))
```


### Exercise 3

The intercept of 3.75 means for female and the people scoring 0 on beauty score, the predicted level of teaching score is 3.75.
The 0.07 estimate of beauty score indicates a positive association between beauty score and teaching score, controlling for gender.
Controlling for beauty score, being a male can lead to a .17 increase in teaching score.

### Exercise 4

5.5%

### Exercise 5

Male

### Exercise 6

3.74 + .07*beauty + .17*1

### Exercise 7

```{r}
lm(score~bty_avg+gender+bty_avg*gender, data = df) |> summary()
```

The positive association is stronger for males than females. 

### Exercise 8

The R squared value increase a little bit. Gender helps us better understand the relationship between beauty and teaching score. 

### Exercise 9

The slope becomes larger after controlling for gender. 


### Exercise 10

```{r}
lm(score~bty_avg+rank, data = df) |> summary()
```


### Exercise 11

I think ethnicity will not have a great predictive power on the teaching scores. While professors of each ethnicity can be a good professor. 

### Exercise 12

```{r}
lm(score~ethnicity, data = df) |> summary()
```

My guess is true. There's no sig association between ethnicity and teaching score. 



### Exercise 13

cls_did_eval should not be included as its information is the same as the conduct of cls_perc_eval and cls_students.

### Exercise 14

```{r}
lm(score~rank+ ethnicity+ gender+ language+ age+ cls_perc_eval+cls_students+ cls_level+ cls_profs+ cls_credits+ bty_avg, data = df) |> summary()
```


### Exercise 15

```{r}
all <- lm(score~rank+ ethnicity+ gender+ language+ age+ cls_perc_eval+cls_students+ cls_level+ cls_profs+ cls_credits+ bty_avg, data=df)
backward <- stats::step(all, direction = "backward", scope = formula(all), trace = 0)
summary(backward)
```


### Exercise 16

While after controlling age, gender, language, credit approach, beauty score and evaluation percentile, ethnicity becomes a significant predictor for teaching score. Being a non-minority teacher will lead to higher teaching score.

Also, the more student finish the evaluation, the higher score the teacher will get.

### Exercise 17

A white, male, handsome professor offering a one-credit evaluation course will receive a high evaluation score from students. 

### Exercise 18

I think some of the conclusion will be generalized to other universities like the positive association between good looking and score, and also the one credit evaluation approach. 

However, I don't think for a university located in more liberal states or cities, the ethnicity and gender may not be a key factor for the course evaluation score.
